Polytope notes

### 2019-12-14 arxiv/poly-embed.tex

>>>>

\begin{proof}[Alternate proof of Lemma \ref{lemma:distance-loss}]
  Let the minimum of $L(\cdot;p)$ be $L^*$.
  Consider the convex set of minimizers of $L$, $U^* = \{u: L(u;p) = L^*\}$.
  Let $B = \{v: \|v\|=1\}$.
  We parameterize points outside $U^*$ by considering all $v \in B$, letting $u^*(v) = \argmax_{u \in U^*} \langle u, v\rangle$.
  For all $v$ such that the argmax exists, we consider the ray $R_v := \{ u^*(v) + \alpha v : \alpha \geq 0\}$.
  We will find a constant $c$ such that, for each ray $R_v$ and each $u = u^*(v) + \alpha v$, we have
  \begin{equation}
    L(u) \geq L^* + (c)(\alpha) = L^* + c d(U^*,u) .  \label{eqn:Lu-geq-const}
  \end{equation}
  \bo{This isn't right because there are multiple possible $u^*(v)$ in general....}

  For each $i$ with $f_i(u) = a_i \cdot u + b_i$, consider the set
    \[ V_i := \{v \in B : f_i(u^*(v)) = L^* \text{ and } a_i \cdot v \geq a_j \cdot v ~ (\forall j: f_j(u^*(v)) = L^*)\}. \]
  We claim
  \begin{enumerate}
    \item There is a $c_i$ such that, for all $v \in V_i$ and all $\alpha \geq 0$, $L(u^*(v) + \alpha v) \geq L^* + \alpha c_i$.
    \item $\cup_{i=1,\dots,k} V_i = \{v: \|v\|_2=1\}$.
  \end{enumerate}
  By definition, for all $v \in V_i$, we have $L(u^*(v) + \alpha v) \geq f_i(u^*(v) + \alpha v) = L^* + (\alpha) a_i \cdot v$.
  So we claim $\inf_{v \in V_i} a_i \cdot v > 0$.
  First, we observe that the infimum is achieved because it is the solution to a set of linear inequalities on a convex, closed, bounded set.
  \bo{Ok?}
  Next, we observe that if $a_i \cdot v \leq 0$ for some $v \in V_i$, then for some small enough $\alpha > 0$, we would have $L(u^*(v) + \alpha v) \leq L^*$, a contradiction with the definition of the optimal set and value of the function.

\end{proof}

### 2019-12-14 notes/bo-separated.tex

  Now, let $U_S' = \text{relint}~U_S$.

  Claim: the set of normals and tangent supporting hyperplanes at $u$ is constant for all $u \in U_S'$, for each $U_S'$.
  Furthermore, each is a closed, convex, bounded (?) set.

>>>>

  For $u \in \text{boundary}~U^*$, let $N(u)$ be the set of unit normal vectors that expose $u$ in $U^*$.
  Let $D(u)$ be the set of subgradients of $L(\cdot;p)$ at $u$.
  Note $N(u)$ and $D(u)$ are closed, convex sets, and $N(u)$ is of course bounded, hence compact.

  Let $U_S' = \text{relint}~U_S$.
  Claim: $N(u)$ and $D(u)$ are constant for all $u \in U_S'$, for each $S$.
